Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-11 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:11	10:31:06	(Tue11.Aug)

- Why?

>>>>

% - Nature and scope
% - Past work
% - Methods
% - Brief summary results
% - Brief conclusions

\IEEEPARstart{T}{he} best adaptive sonars are found in nature. Bats, for instance, use a high frequency sonar to detect, identify and track prey with amazing precision in caves amongst a myriad of other bats. In comparison, most human made active sonars inhibit a static behaviour when they collect data, but
